Essays in \\Computational Management Science

### 2018-04-26 Chapters/Chapter01.tex
Minor abstract and SDM changes.

Despite Bitcoin's huge success, there are still many challenges to be overcome. We will focus on one specific of those challenges: scaling. One important challenge that we will skip is to reduce the size of the ledger (or blockchain), which today is around 125GB and is growing at a rate of 4.5GB per month \citep{blockchaininfosize}.

@@

@@

Generating new transactions in Bitcoin has a tiny cost because one only has to generate the transaction itself, digitally sign it, and propagate in the Bitcoin network. On the one hand, it means that any device is capable of generating new transactions, but, on the other hand, it makes Bitcoin susceptible to spam attacks. One may generate hundreds of thousands of new valid transactions, overloading the unconfirmed transactions pool and saturating the network.

>>>>

Despite Bitcoin's huge success, there are still many challenges to be overcome. We will focus on the following of those challenges: scaling, spamming, and centralization. One important challenge that we will skip is to reduce the size of the ledger (or blockchain), which today is around 125GB and is growing at a rate of 4.5GB per month \citep{blockchaininfosize}.

@@

The scaling problem is not precisely an issue of Bitcoin, but an issue of the Blockchain technology. Hence, all other Blockchain-based cryptocurrencies have the same limitations, such as Litecoin, Bitcoin Cash, and Ethereum. One may arguee that increasing the block size is a feasible solution to scaling, but I would reply that it is a temporary solution which buys some time until the next network saturation.

@@

Generating new transactions in Bitcoin has a tiny computational cost because one only has to generate the transaction itself, digitally sign it, and propagate it in the Bitcoin network. On the one hand, it means that any device is capable of generating new transactions, but, on the other hand, it makes Bitcoin susceptible to spam attacks. One may generate hundreds of thousands of new valid transactions, overloading the unconfirmed transactions pool and saturating the network.

### 2018-04-26 FrontBackmatter/Abstract.tex
Minor abstract and SDM changes.

\vfill

\pdfbookmark[1]{Resumo}{Resumo}
\chapter*{Resumo}
Aqui entre o resumo\dots

@@

\vfill

>>>>

%\vfill

\chapter*{Resumo}
A presente tese é formada por três trabalhos científicos na área de Management Science Computacional. A gestão moderna e a alta tecnologia interagem em múltiplas e profundas formas. O professor Andre Ng diz aos seus estudantes na Escola de Negócios de Stanford que ``Inteligência Artificial é a nova eletricidade'', como sua forma hiperbólica de enfatizar o potencial transformador da tecnologia.

O primeiro trabalho é inspirado na possibilidade de que haverá alguma forma de dinheiro digital e estuda ledger distribuídas, propondo e analisando o Hathor, uma arquitetura alternativa para criptomoedas escaláveis.

O segundo trabalho pode ser um item crucial no entendimento de tomadas de decisão, nos trazendo um modelo formal de \emph{recognition-primed decisions}. Situada na intersecção entre psicologia cognitiva, ciência da computação, neuro-ciência e inteligência artifical, ele apresenta um framework open-source, multi-plataforma e altamente paralelo da Sparse Distributed Memory e analisa a dinâmica da memória e algumas aplicações.

O terceiro e último trabalho se situa na intersecção entre marketing, difusão de inovação tecnologica e modelagem, extendendo o famoso modelo de Bass para levar em consideração usuário que, após adotar a tecnologia por um tempo, decidiram rejeitá-la.

@@

%\vfill
